---
title: "Mapping CARE Regions"
subtitle: "A Brief Introduction, using Mapview"
output:
  html_document:
    toc: true
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Mapping impact and exceedance polygons with mapview}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Introduction

Let's begin with something that's easy to "see".

- The `CARE` package provides some handy "geodata"
- Revealed in the maps that follow

```{r message = FALSE}
library(CARE)
```

The main thing of interest is called `CARE_region_geodata` ...

```{r CARE_region_geodata, echo = TRUE, message = FALSE}
show(CARE_region_geodata) # full menu = `data(package = "CARE")`
```

Let's see that in map form ...

```{r mapview-CARE_region_geodata}
mapview(CARE_region_geodata, zcol = "CARE_designation")
```

## Basic Filtering

You can `filter` this geodata, just like any tabular data ...

```{r impact_regions}
impact_regions <- filter(CARE_region_geodata, CARE_designation == "impact")
mapview(impact_regions, zcol = "CARE_name")
```

```{r exceedance_regions, echo = TRUE}
exceedance_regions <- filter(CARE_region_geodata, CARE_designation == "exceedance")
mapview(exceedance_regions, zcol = "CARE_name")
```

Let's `filter` again, this time by `CARE_name`.

```{r CARE_Pbg_regions}
Pbg_area_names <- c("Pittsburg", "Bethel Island")
CARE_Pbg_regions <- filter(CARE_region_geodata, CARE_name %in% Pbg_area_names)
mapview(CARE_Pbg_regions, zcol = "CARE_name")
```

## You Can Do GIS with R

You can *union*, *intersect*, and anything else you can think of. Let's union ...

```{r Pbg_boundary}
Pbg_boundary <- st_union(CARE_Pbg_regions)
mapview(Pbg_boundary)
```

## How Should I Learn More?

Two great places to start/explore, and to keep coming back to:

- Comprehensive "Task Views" (via CRAN): [Spatial](https://cran.r-project.org/web/views/Spatial.html) and [Spatiotemporal](https://cran.r-project.org/web/views/SpatioTemporal.html)
- The [`mapview`](https://github.com/r-spatial/mapview) package, a good bridge for ArcGIS or QGIS "explorers"
- The [`sf`](https://github.com/r-spatial/sf) package, for (modern) technical fundamentals of spatial data in R
